Incentivizing Exploration with Unbiased History

### 2018-11-01 2level.tex
.

%!TEX root = main.tex
\section{Warm-up: full-disclosure paths}

We first consider a disclosure policy that reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}. The info-path for this policy is a simple path. We use this policy as a ``gadget" in our constructions. Hence, we formulate it slightly more generally:

>>>>

%!TEX root = main.tex
\section{Warm-up: full-disclosure paths}
\label{sec:warmup}
We first consider a disclosure policy that reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}. The info-path for this policy is a simple path. We use this policy as a ``gadget" in our constructions. Hence, we formulate it slightly more generally:
